Distributed Version Control Systems

### 2010-06-06 laarsample.tex
Agregado un detalle sobre tool support

With these DVCS, tool support and various plugins just isn't as 
mature as systems like SVN, which are more mature and well tested. 
Git, in particular, is biased on Linux and doesn't really work out of the box in Windows, but works with Cygwin. 
Mercurial is much more portable, but some tools are also incomplete, like hg-subversion (a tool 
to interoperate with svn). Git has git-svn which allows to push and pull from svn repositories, 
easing transitions.

>>>>

Systems like SVN have mature tool support and various plugins, but popular DVCS are catching up.
For these tools most complete interface is the command line, but for the usual operations, 
there are various visual tools to operate with the repository.
Git, in particular, is based on Linux and originally didn't work work out of the box in Windows, 
but with Cygwin. 
Now there is a fork of Git that ports it to windows, but the linux heritage is 
shown and the installation includes a Bash shell. 
Git also includes a portable GUI written in Tk, invoked with command ``git gui'' 
but while it is simple and easy to use, it is very incomplete (for example, 
it doesn't include the ``pull'' operation, among others).

Mercurial is much more portable, but some tools are also incomplete, like hg-subversion (a tool 
to interoperate with svn). Git has git-svn which allows to push and pull from svn repositories, 
easing transitions.

### 2010-06-06 paper.tex
Configurada la separacion entre columnas
Agregado un detalle sobre tool support

With these DVCS, tool support and various plugins just isn't as 
mature as systems like SVN, which are more mature and well tested. 
Git, in particular, is biased on Linux and doesn't really work out of the box in Windows, but works with Cygwin. 
Mercurial is much more portable, but some tools are also incomplete, like hg-subversion (a tool 
to interoperate with svn). Git has git-svn which allows to push and pull from svn repositories, 
easing transitions.

>>>>

Systems like SVN have mature tool support and various plugins, but popular DVCS are catching up.
For these tools most complete interface is the command line, but for the usual operations, 
there are various visual tools to operate with the repository.
Git, in particular, is based on Linux and originally didn't work work out of the box in Windows, 
but with Cygwin. Now there is a fork of Git that ports it to windows, but 
Mercurial is much more portable, but some tools are also incomplete, like hg-subversion (a tool 
to interoperate with svn). Git has git-svn which allows to push and pull from svn repositories, 
easing transitions.
